Equilibria and Convergence of Fictitious Play on Network Aggregative Games

### 2021-05-24 Documents/FP in NAGs/neurips_2021.tex
Included Bib File for Neurips

\begin{abstract}
  Understanding the long term behaviour of learning algorithms is an important object of study if we are to design systems which can be considered safe. However, as the number of players in a game increase, it is known that the dynamics of learning becomes increasingly chaotic. As such, the most rigorous results of learning dynamics are limited to two player games.

  In this study, we contribute towards the study of learning with multiple agents. We do this through the introduction of learning on network aggregative games, in which each player's reward is dependent on its own strategy and a convex combination of its neighbours. In particular, we present a continuous time analysis of the Fictitious Play learning dynamic on such a game. We reach a number of conclusions. In particular, we show that Fictitious Play reaches a fixed point when the game is zero-sum and provide conditions under which this fixed point corresponds to a Nash Equilibrium. In addition, we show that agents learning through Fictitious Play achieve no-regret, regardless of the choice of game. Finally, we present experimental evidence of a family of games for which Fictitious Play reaches a limit cycle and evidence that the introduction of noise has the potential to break this cyclic behaviour and allow agents to reach the Nash Equilibrium.
\end{abstract}

@@

Multi-Agent Learning \cite{Schwartz} requires a number of agents to adapt in an environment where
each agent must adapt in response to the behaviour of the other agents. This leads to a
fundamentally non-stationary problem, which presents a challenge to designing effective learning
policies. Even when there are a small number of agents in the game, learning has been shown to lead
to non-stationary, and even chaotic behaviour \cite{SatoChaos}, and this problem becomes even more
pronounced as the number of agents increase \cite{Sanders}. In this light, it would seem that, when there is a large population of agents, it is almost impossible to understand the long term behaviour of multi-agent learning \cite{PiliourasChaoticMaps}. This, of course, poses a problem for AI safety, for which it is desirable that learning systems are designed so that their ultimate behaviour is guaranteed to satisfy some predetermined goals.

To deal with this problem, one must attempt to reduce the many player game to something which is
tractable. A number of reductions have been proposed, most notably \emph{Mean Field} Games
and \emph{Aggregative} Games. The former makes the assumption of an infinite
number of agents, so that the population can be represented through a distribution over players'
states \cite{CainesPaper} . Every agent then updates their action profiles depending on this
distribution. In the latter each agent considers a real valued function which is a convex
combination of the states of the other agents. Both formulation allows for a many player game to be reduced to a set of two-player games.

Both formulations have been the object of rigorous study and it has been shown that agents reach an equilibrium when learning on such games (c.f. \cite{MFGLearningPapers} for Mean Field Games and
\cite{Aggregative Papers} for Aggregative Games). However, both also present a fundamental limitation.
Namely, they both require that agents have access to the action profiles of the entire population.
This could be through communication with all other agents, or through the intervention of a central
coordinator who is able view the entire population. Whilst recent work aims to relax this assumption
through the introduction of noise \cite{MFG-FP} or partial observability \cite{AAMASPaper}, the
requirement that each agent updates their actions based on the entire population is rather strong and not always supported by empirical evidence.

In this study, we investigate a variant of the aggregative game known as the \emph{Network
Aggregative} (NA) Game. This format assumes that there is an underlying communication network
through which agents interact. Then each agent updates their actions according only to those agents
with whom they communicate. This significantly relaxes the communication load on each agent and
lifts the need for a central coordinator. Recent work on the NA game has shown that it is possible
for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Grammatico,
LeaderFollower, MyopicAgents}. We contribute in this direction by analysing the long term behaviour of learning on an NA game. In particular, we analyse the Fictitious Play Learning
Algorithm \cite{Brown, Harris}, in which agents are assumed to be myopic, in that they react solely
to the previous behaviour of the others.

@@

The NA game is a recent introduction \cite{Parise2015} which presents a variant of aggregative games
by adding an underlying structure to the population. Since its introduction, distributed algorithms
have been built with the aim of finding NE. In particular, \cite{Parise2015, Parise2020} consider
the case in which payoffs are given by Lipschitz functions with unique minimisers and apply standard
topological fixed point towards designing algorithms which will converge to the NE. We note that the
\emph{Mann Iteration}, one of the algorithms applied in \cite{Parise2020} shares a remarkably
similar form with the discrete variant of FP. To the best of our knowledge, this link has not been
explored in the literature and is an avenue for research which we are currently pursuing. Another
common algorithm for distributed NE seeking is the projected gradient (resp. subgradient) dynamics
which is explored in \cite{Zhang2020} (resp. \cite{Shokri2020, Shokri2021}). In all of these works,
the cost function is assumed to be convex, and therefore have a unique minimiser. In fact this is a
common assumption in works concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due to
its ubiquity in control settings. We have not yet come across works which consider NA games from the
point of view of payoff matrices, which are more common in multi-agent learning settings.
Furthermore, to the best of our knowledge, this is the first work which introduces the application
of a learning algorithm in the NA setting.

@@

Fictitious Play was introduced by Brown in 1951 \cite{BrownPublished, BrownUnpublished} as a
'natural' way in which to approximate the Nash Equilibrium in zero sum games. It was known at the
time that a discrete variant of the algorithm would converge to the NE in two player zero-sum games
\cite{Robinson}. Since then a number of proofs of convergence were determined in 2 player games
\cite{Miyasawa, Polak, Berger, Monderer and Sela, Monderer and Shapley}, as well as corresponding
convergence rates \cite{Harris, Shapiro}. Many results hold for both the discrete and continuous
variants of FP. Their relation was finally solved by Hofbauer \cite{Hofbauer}, who showed that
attractors of the discrete time process are also attractors for the continuous time variant. As
such, most of the analysis on FP focuses on the continuous time variant \cite{Ostrovski}. It was
later shown in \cite{Shapley} that there is a family of games (now called the \emph{Shapley family})
for which FP does not converge at all but rather shows periodic behaviour. However, the work looking at fictitious play
where there are more than two agents is sparse. \cite{Sela} considers a game in which a multi-player
game is decomposed by requiring that each agent engage in a two person game against each of the
opponent. Their payoff is given by the sum of payoffs in all of these subgames. It was found that,
if this game is zero sum, then FP will converge. Similar results for more than two players were
found for games where all agents share the same payoff in \cite{MondererShapley1994}. In \cite{FPMFG}, the action
of FP was considered in a Mean Field Game, and it was found again that the algorithm converges for
zero sum games. The most general result, and the one most similar to our own, was found by Ewerhart
and Valkanova in 2020 \cite{Ewerhart} in which they showed that fictitious play converges in network
games, where each agent is engaged in a two-player game with each of their neighbours. The rate of
convergence was found to be independent of the network size.  Our work extends the analysis of FP in
multiplayer games by considering its action in NA Games, so that the agents do not play individual
games against each of their neighbours but rather a single game against the aggregate of their
neighbours. In particular we also extend a result for two player games found by Ostrovski and van
Strein \cite{Payoff Performance} which showed that FP achieves no-regret to the multi-player
setting.

@@

  The model we consider is that there is a set $\agentset = {1,
           \ldots , N}$ of agents who are connected through an underlying
          interaction graph. This graph is given by the tuple
          $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
          the set of all pairs $(\mu, \nu) \in \agentset \times \agentset$
          connected. Formally,

  \begin{definition}[Interaction Graph]
    Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset,
    \weightset))$ such that
    \begin{itemize}
    \item $\edgeset \subseteq \agentset \times \agentset$.        Then, the set of neighbours of agent
        $\mu$ is denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu, \nu) \in \edgeset\}$.
      \item $\weightset \in M_N(\mathbb{R})$ is the weighted adjacency matrix whose elements $w^{\mu
        \nu}$ expresses the importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not
        \in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
    \end{itemize}
  \end{definition}

  With the above definition, we can formalise the network aggregative (NA) game:

  \begin{definition}[Network Aggregative Game]
    A Network Aggregative game is defined as the tuple $\Gamma = (I, (\actionset{\mu},
        \utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is the interaction graph,
        $\actionset{\mu}$ and $\utility{\mu}$ refer to $\mu$'s set of actions (with cardinality
        $|\actionset{\mu}| = n$) and utility function respectively.
  \end{definition}

  We consider the \emph{state} of agent $\mu$ to be the probability vector $\xmu \in
  \mathbb{R}^n$ where $\xmu_i$ is the probability with which the agent plays action $i$. It
  should be noted that this probability vector is often referred to as $\mu$'s \emph{mixed
  strategy}. With this in mind, we can construct, as their state space, the unit simplex on
  agent $\mu$'s action set. This is given as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \,
  \sum_i \xmuaction{i} = 1\}$. Also associated with each agent is a utility function

  The utility function, for each agent $\mu$, is given as $u^\mu(\xmu, \xnotmu)$ in which we use
  the standard notation $-\mu$ to refer to all agents other than $\mu$. Notice that this requires
  that each agent play the same strategy against all of their neighbours. What is unique about the
  NA game is the structure of the payoffs themselves. In this format, each agent is receives a
  reference $\sigma$ which is a weighted sum of each of their neighbours
  state. Formally
  %
  \begin{equation}
    \sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
  \end{equation}

  Then, the agent's must optimise their payoff with respect to this reference vector. Thus,
  instead of having to consider the actions of the entire population, or play individual games
  against each of their neighbours, the agent only has to consider $\sigma^\mu$ as a
  `measurement' of the local aggregate state and optimise with respect to this measurement.
  This allows us to make the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In
  particular, we consider that the agent is engaged in a matrix game against the
  reference vector so that
  %
  \begin{equation}
    u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu
                \cdot A^\mu \weightedsum.
  \end{equation}

  where $A^\mu$ is the payoff matrix associated to agent $\mu$. Note that this means we can write
  the game $\Gamma$ with the payoff matrices $A^mu$ in place of the utility functions
  $\utility{\mu}$. The NA game allows for the reduction of a multiplayer game into a series of
  two-player games. The agent's goal is to maximise their payoff with respect to the reference
  vector. As such, we define the best response correspondence $BR^\mu$ which maps any $\refmu$
  the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$.

  Finally, a central concept of game theory is that of the Nash Equilibrium, in which no rational
  agent has the incentive to deviate from their current state. This can be formalised by saying
  that all agents are playing the best response to each other.

  This leads naturally to the definition of a Nash Equilibrium in an NA Game as

  \begin{definition}(NE) \label{def::NE}
    The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is an NE if, for all $\mu$,  
    \begin{equation*}
    \NE{\mu} \in BR^\mu (\refmu) = \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
    \end{equation*} 
  \end{definition}

  \begin{remark}
    It can be seen that the concept of the Nash Equilibrium in the NA game is a natural
    extension of the NE in a bimatrix game $(A, B)$. In particular, if we consider an NA game
    with only two players and no self-loops then the above definition yields

    \begin{equation*}
      \NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2}), 
    \end{equation*}

    and similarly for $\NE{2}$. This is precisely the definition of an NE in a two player game \cite{}.
  \end{remark}

  We will show that the NE exists for an NA game in Section \ref{sec::ExistenceofNE}.

  Finally we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally

  \begin{equation}
    \sum_\mu u^\mu(\xmu, \weightedsum) = 0.
  \end{equation}

@@

  Fictitious Play requires that, at the current time, each agent considers the average state
  of their opponent in the past, and respond optimally (i.e. play a best response) to this state. In the case of an NA game, each agent considers their reference vector to be their
  opponent. As such, each agent $\mu$ must update their state according to the time-average of
  $\refmu$. To formalise this we write

@@

  Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
  Fictitious Play in continuous time, but with a slight adaptation for the NA game.
%
  \begin{definition}[Network Aggregative - Continuous Time Fictitious Play (NA-CTFP)]
    An NA-CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
    and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
    BR^\mu(\alpha_{\sigma}^\mu)$ for almost all $t \geq 1$.
  \end{definition}

@@

    In this manner, the $\alpha^\mu(t; m)$ denotes the time average of the strategies played by
    agent $\mu$ up to time $t$ when the strategies are given by $\xmu(t)$. Note that we often reduce the notation to $\alpha^\mu(t)$. Then, fictitious play requires that the agents update their
    strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in BR^2(\alpha^1(t))$. It can be
    seen, therefore, that the NA-CTFP is a natural extension of CTFP in the classical
    two-player setting \cite{}.
  \end{remark}

@@

  \begin{assumption}\label{ass::rowstochastic}
    The weighted adjacency matrix $\weightset$ is constant and \emph{row stochastic} meaning
    that the sum elements in each row of $\weightset$ is equal to one. This assumption is
    made to ensure that the analysis of NA games can be derived as a natural extension to the
    classical setting of two-player games. We can think of the row stochastic condition as the
    ability of each agent to prioritise the state information it receives from each of its
    neighbours. It is also a classical assumption made in the analysis of network games
    \cite{one of the network game papers} and can is straightforward to implement \cite{Eyad}.
  \end{assumption}

  \begin{assumption}\label{ass::matrixgame}
    The payoffs are given through matrix games and, therefore, are bilinear. Payoff matrices
    have a rich history in game theory and has generated a number of prototypical examples for
    economic study including the Prisoner's Dilemma game (see \cite{Axelrod} for an interesting
    implementation of this). They also allow for the design of multi-agent systems in
    computational settings, particularly in the case of task and resource allocation \cite{AGT
    and some of the Applied Game Theory Papers}. It should be noted, however, that game
    theoretic analysis is starting to consider various other forms of utility functions,
    including monotone \cite{Maryam} and convex \cite{Parise}. We believe that the analysis of
    Fictitious Play should follow in these developments and we consider it as an important area
    of future work.
  \end{assumption}

  \begin{assumption}\label{ass::sameactions}
    The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
    a classical assumption which is made in most game theoretic settings and includes, as a
    special case, the analysis of homogeneous agents \cite{}. However, it should be noted that,
    in \cite{Ewerhart}, CTFP was analysed without this requirement.  
  \end{assumption}

@@

\section{Convergence of Fictitious Play}

@@

  In this section we aim to find some convergence structure for the
  case in which the NA game is not necessarily zero-sum. In
  particular, we show that the NA-CTFP process converges to the set of
  coarse correlated equilibria \cite{}.
  %
  \begin{definition}
    A distribution $\mathcal{D}$ over the joint action set $S =
    \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
    (CCE) if, for all $\mu$
    \begin{equation}
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
      \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{-
          \mu})] \hspace{1cm} \forall j \in S^\mu.
    \end{equation}
  \end{definition}

@@

  \begin{remark}
    As usual, the notion of CCE in an NA game is a natural extension of the CCE for two player
    games. In fact, if we consider the NA game to be a two player game with no self-loops, then
    we recover exactly the definition of the CCE set in two player games \cite{PayoffPerformance}.
  \end{remark}

  \begin{remark}
    The notion of the CCE set is related to the idea of \emph{average external regret} (for the
    sake of brevity we drop the term `external' and refer the reader to \cite{AGT}). Here, we
    will present what is meant by average regret and state that if at some time $T$ all agents'
    average regret is non-positive, then the game is said to have reached the CCE set. The
    reader should consult \cite{PayoffPerformance} for an excellent exposition regarding the
    link between the CCE set and average regret in two player games which, of course, extends
    naturally to the NA game.

@@

    in which $\pure{\mu}{i}$ denotes the probability vector in $\Delta_\mu$ with $1$ in the slot
    $i'$ and $0$ everywhere else. Note, this is the \emph{average regret} for the agent $\mu$
    and, of course, can be related to the \emph{cumulative regret} which is used for analysis
    in \cite{Leonardos and Piliouras, Cesa-Bianchi}.  To illustrate the average regret, let us
    consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
    is given by

@@

  As a example of nonconvergence we consider the Shapley family of games \cite{}. In a two player bimatrix game $(A_\beta, B_\beta)$ this is given by

@@

  where $\beta \in (0, 1)$. In \cite{} this was shown to produce both periodic and chaotic behaviour for different choices of $\beta$.

@@

\section*{References}

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references.
{\bf Note that the Reference section does not count towards the eight pages of content that are allowed.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
(eds.), {\it Advances in Neural Information Processing Systems 7},
pp.\ 609--616. Cambridge, MA: MIT Press.

>>>>

\begin{abstract}
Understanding the long term behaviour of learning algorithms is an important object of study if we are to design systems which can be considered safe.In this study, we contribute towards the study of learning with multiple agents. We do this through the introduction of learning on network aggregative games, in which each player's reward depends only on its own strategy and a convex combination of its neighbours. In particular, we present a continuous time analysis of the Fictitious Play learning dynamic on such a game. We show that Fictitious Play reaches a fixed point when the game is zero-sum and provide conditions under which this fixed point corresponds to a Nash Equilibrium. In addition, we show that agents learning through Fictitious Play achieve no-regret, regardless of the choice of game. Finally, we present experimental evidence of a family of games for which Fictitious Play reaches a limit cycle and evidence that the introduction of noise has the potential to break this cyclic behaviour and allow agents to reach the Nash Equilibrium.
\end{abstract}

@@

Multi-Agent Learning \cite{Schwartz2014} requires a number of agents to adapt in an environment where
each agent must adapt in response to the behaviour of the other agents. This leads to a
fundamentally non-stationary problem, which presents a challenge to designing effective learning
policies. Even when there are a small number of agents in the game, learning has been shown to lead
to non-stationary, and even chaotic behaviour \cite{Sato2002}, and this problem becomes even more
pronounced as the number of agents increase \cite{Sanders2018}. In this light, it would seem that, when there is a large population of agents, it is almost impossible to understand the long term behaviour of multi-agent learning \cite{Chotibut2021}. This, of course, poses a problem for AI safety, for which it is desirable that learning systems are designed so that their ultimate behaviour is guaranteed to satisfy some predetermined goals.

To deal with this problem, one must attempt to reduce the many player game to something which is
tractable. A number of reductions have been proposed, most notably \emph{Mean Field} Games
and \emph{Aggregative} Games. The former makes the assumption of an infinite
number of agents, so that the population can be represented through a distribution over players'
states \cite{Huang2006} . Every agent then updates their action profiles depending on this
distribution. In the latter each agent considers a real valued function which is a convex
combination of the states of the other agents. Both formulation allows for a many player game to be reduced to a set of two-player games.

Both formulations have been the object of rigorous study and it has been shown that agents reach an equilibrium when learning on such games (c.f. \cite{Perrin2020} for Mean Field Games and
\cite{Jensen2010, DePersis2020, Parise2020} for Aggregative Games). However, both also present a fundamental limitation.
Namely, they both require that agents have access to the action profiles of the entire population.
This could be through communication with all other agents, or through the intervention of a central
coordinator who is able view the entire population. Whilst recent work aims to relax this assumption
through the introduction of noise \cite{Perrin2020} or partial observability \cite{Elie2020}, the
requirement that each agent updates their actions based on the entire population is rather strong and not always supported by empirical evidence.

In this study, we investigate a variant of the aggregative game known as the \emph{Network
Aggregative} (NA) Game. This format assumes that there is an underlying communication network
through which agents interact. Then each agent updates their actions according only to those agents
with whom they communicate. This significantly relaxes the communication load on each agent and
lifts the need for a central coordinator. Recent work on the NA game has shown that it is possible
for agents to reach an equilibrium strategy in an entirely distributed manner \cite{Koshal2016, Shokri2020, Shokri2021, Parise2015}. We contribute in this direction by analysing the long term behaviour of learning on an NA game. In particular, we analyse the Fictitious Play Learning
Algorithm \cite{Brown1949, Harris1998}, in which agents are assumed to be myopic, in that they react solely
to the previous behaviour of the others.

@@

The NA game is a recent introduction \cite{Parise2015} which presents a variant of aggregative games
by adding an underlying structure to the population. Since its introduction, distributed algorithms
have been built with the aim of finding NE. In particular, \cite{Parise2015, Parise2020} consider
the case in which payoffs are given by Lipschitz functions with unique minimisers and apply standard
topological fixed point towards designing algorithms which will converge to the NE. Another
approach for distributed NE seeking is the projected gradient (resp. subgradient) dynamics
which is explored in \cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all of these works,
the cost function is assumed to be convex, and therefore have a unique minimiser. In fact this is a
common assumption in works concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due to
its ubiquity in control settings. We have not yet come across works which consider NA games from the
point of view of payoff matrices, which are more common in multi-agent learning settings.
Furthermore, to the best of our knowledge, this is the first work which introduces the application
of a learning algorithm in the NA setting.

@@

Fictitious Play was introduced in 1951 \cite{Brown1949} as a
'natural' way in which to approximate the Nash Equilibrium in zero sum games. It was known at the
time that a discrete variant of the algorithm would converge to the NE in two player zero-sum games
\cite{Robinson1951}. Since then a number of proofs of convergence were determined in 2 player games
\cite{Miyasawa1961, Metrick1994, Berger2007, Monderer1997, Monderer1996}. Many results hold for both the discrete and continuous variants of FP. However, the work looking at FP
where there are more than two agents is sparse. \cite{Sela1999} considers a game in which a multi-player
game is decomposed by requiring that each agent engage in a two person game against each of the
opponent. Their payoff is given by the sum of payoffs in all of these subgames. It was found that,
if this game is zero sum, then FP will converge. Similar results for more than two players were
found for games where all agents share the same payoff in \cite{Monderer1996}. In \cite{Perrin2020}, the action
of FP was considered in a Mean Field Game, with convergence in
zero sum games. The most general result, and the one most similar to our own, was found by Ewerhart
and Valkanova in 2020 \cite{Ewerhart2020} in which it was found that FP converges in network
games, where each agent is engaged in a two-player game with each of their neighbours Our work extends the analysis of FP in
multiplayer games by considering its action in NA Games, so that the agents do not play individual
games against each of their neighbours but rather a single game against the aggregate of their
neighbours. In particular we also extend a result for two player games found by Ostrovski and van
Strien \cite{Ostrovski2014} which showed that FP achieves no-regret to the multi-player
setting.

@@

The model we consider consists of
%is that there is
a set $\agentset = \{1,
\ldots , N \}$ of agents, who are connected through an underlying
interaction graph.
%This graph is given by the tuple
%$(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
%the set of all pairs $(\mu, \nu) \in \agentset \times \agentset$
%connected.
More formally:
%        
\begin{definition}[Interaction Graph] \label{interactiongraph}
	Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset,
	\weightset))$ is such that
	\begin{itemize}

		\item $\edgeset \subseteq \agentset^2$.  Then, the set of
		neighbours of agent $\mu$ is denoted as $N^\mu = \{\nu \in
		\agentset \mid (\mu, \nu) \in \edgeset\}$.

		\item $\weightset \in M_N(\mathbb{R})$ is the weight adjacency matrix, whose elements $w^{\mu
			\nu} \in [0, 1]$ expresses the importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not
		\in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
	\end{itemize}
\end{definition}

Given Def.~\ref{interactiongraph} of interaction graph,
%With the above definition,
we introduce network aggregative (NA) games:
%
\begin{definition}[NA Game]
	A {\em network aggregative game} is
	%defined as the
	a tuple $\Gamma = (I, (\actionset{\mu},
	\utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is an
	interaction graph, and for every agent $\mu \in \mathcal{N}$, $\actionset{\mu}$ and $\utility{\mu}$
	%refer to
	are $\mu$'s set of actions (with cardinality $|\actionset{\mu}| = n$)
	and utility function respectively.
\end{definition}

We define the \emph{state} of agent $\mu$ to be the probability
vector $\xmu \in \mathbb{R}^n$, where $\xmu_i$ is the probability
with which agent $\mu$ plays action $i$.
%It should be noted that
This
probability vector is often referred to as $\mu$'s \emph{mixed
	strategy}. With this in mind, we can construct, as their state
space, the {\em unit simplex} $\Delta_\mu$ on agent $\mu$'s action set, which
is defined
as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \, \sum_i
\xmuaction{i} = 1\}$. Also associated with each agent is a utility
function

The utility, for each agent $\mu$ and action profile
$(\xmu, \xnotmu)$, is given as $u^\mu(\xmu, \xnotmu)$ in which we
use the standard notation $-\mu$ to refer to all agents other than
$\mu$. Notice that this requires that each agent plays the same
strategy against all of their neighbours. What is unique about 
NA games is the structure of the payoffs themselves. In this format,
each agent $\mu$ receives a reference $\sigma^{\mu} = \sum_{\nu \in N^\mu} \wmunu \xnu$, which is a weighted sum
of each of their neighbours state.
%Formally
%
%  \begin{equation}
%    \sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
%  \end{equation}

Then, the agent must optimise their payoff with respect to the
reference vector $\sigma^{\mu}$. Thus, instead of considering
the actions of the entire population, or play individual games
against each of their neighbours, the agent only considers
$\sigma^\mu$ as a `measurement' of the local aggregate state and
optimises with respect to this measurement.  This allows us to make
the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In
particular, we consider that the agent is engaged in a matrix game
against the reference vector so that
%
\begin{equation}
	u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu
	\cdot A^\mu \weightedsum.
\end{equation}
%
where $A^\mu$ is the payoff matrix associated with agent $\mu$. In particular,  this means we can write the game $\Gamma$ with the payoff
matrices $A^\mu$ in place of the utility functions
$\utility{\mu}$. Hence, the NA game allows for the reduction of a
multi-player game into a series of two-player games. The agent's goal
is to maximise their payoff with respect to the reference vector. As
such, we define the best response correspondence $BR^\mu$, which maps
every $\refmu$ to the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y,
	\refmu)}$.

Finally, a central concept of game theory is that of the Nash
Equilibrium, in which no rational agent has the incentive to deviate
from their current state. This can be formalised by saying that all
agents are playing their best response to each other.
%
This leads naturally to the definition of a Nash Equilibrium in an NA game as
%
\begin{definition}(NE) \label{def::NE}
	The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is a {\em
		Nash equilibrium} if, for all $\mu$,
	\begin{equation*}
		\NE{\mu} \in BR^\mu (\refmu) = \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
	\end{equation*} 
\end{definition}

\begin{remark}
	%It can be seen that
	The notion of Nash equilibrium in the NA game is a natural
	extension of the NE in a bimatrix game.
	%$(A, B)$.
	In particular, if we consider an NA game with only two players and no
	self-loops then the above definition yields that $ \NE{1}$ is an NE iff
	%
	%    \begin{equation*}
	$     \NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2})$,
	%    \end{equation*}
	%
	and similarly for $\NE{2}$. This is precisely the definition of an NE in a two player game \cite{}.
\end{remark}

We will show that the NE exists for an NA game in Section \ref{sec::CTFPAnalysis}.

Finally, we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally,
%
%  \begin{equation}
$\sum_\mu u^\mu(\xmu, \weightedsum) = 0$.
%  \end{equation}

@@

  Fictitious Play requires that, at the current time, each agent considers the average state
  of their opponent in the past, and respond optimally (i.e. play a best response) to this state. In the case of an NA game, each agent considers their reference vector to be their
  opponent. As such, each agent $\mu$ must update their state according to the time-average of
  $\refmu$. To formalise this we define $\avgref{\mu}$ as the time average of agent $\mu$'s reference $\refmu$ up until time $t$.

@@

  Using this, we follow in the footsteps of Ewerhart \cite{Ostrovski2014} and Harris \cite{Harris1998} to define
  Fictitious Play in continuous time, but with a slight adaptation for the NA game.
%
  \begin{definition}[Network Aggregative - Continuous Time Fictitious Play (NA-CTFP)]
    An NA-CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
    and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
    BR^\mu(\alpha_{\sigma}^\mu)$ for almost all $t \geq 1$.
  \end{definition}

@@

    In this manner, the $\alpha^\mu(t; m)$ denotes the time average of the strategies played by
    agent $\mu$ up to time $t$ when the strategies are given by $\xmu(t)$. Note that we often reduce the notation to $\alpha^\mu(t)$. Then, fictitious play requires that the agents update their
    strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in BR^2(\alpha^1(t))$. It can be
    seen, therefore, that the NA-CTFP is a natural extension of CTFP in the classical
    two-player setting \cite{Hofbauer2006}.
  \end{remark}

@@

  \begin{assumption}\label{ass::rowstochastic}
    The weighted adjacency matrix $\weightset$ is constant and \emph{row stochastic} meaning
    that the sum elements in each row of $\weightset$ is equal to one. This assumption is
    made to ensure that the analysis of NA games can be derived as a natural extension to the
    classical setting of two-player games. We can think of the row stochastic condition as the
    ability of each agent to prioritise the state information it receives from each of its
    neighbours. It is also a classical assumption made in the analysis of networks
    and is straightforward to implement \cite{Mai2019}.
  \end{assumption}

  \begin{assumption}\label{ass::matrixgame}
    The payoffs are given through matrix games and, therefore, are bilinear. Payoff matrices
    have a rich history in game theory and has generated a number of prototypical examples for
    economic study including the Prisoner's Dilemma game (see \cite{Axelrod1980} for an interesting
    implementation of this). They also allow for the design of multi-agent systems in
    computational settings, particularly in the case of task and resource allocation \cite{Nisan2007}. It should be noted, however, that game
    theoretic analysis is starting to consider various other forms of utility functions,
    including monotone \cite{Tatarenko2020} and convex \cite{Parise2020}. We believe that the analysis of
    Fictitious Play should follow in these developments and we consider it as an important area
    of future work.
  \end{assumption}

  \begin{assumption}\label{ass::sameactions}
    The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
    a classical assumption which is made in most game theoretic settings and includes, as a
    special case. However, it should be noted that,
    in \cite{Ewerhart2020}, CTFP was analysed without this requirement.  
  \end{assumption}

@@

\section{Convergence of Fictitious Play}
\label{sec::CTFPAnalysis}

@@

  In this section we aim to find some convergence structure for the
  case in which the NA game is not necessarily zero-sum. In
  particular, we show that the NA-CTFP process converges to the set of
  coarse correlated equilibria \cite{Nisan2007}.
  %
  \begin{definition}
    A distribution $\mathcal{D}$ over the joint action set $S =
    \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
    (CCE) if, for all $\mu$
    \begin{equation}
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
      \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{-
          \mu})] \hspace{1cm} \forall j \in S^\mu.
    \end{equation}
  \end{definition}

@@

  \begin{remark}
    As usual, the notion of CCE in an NA game is a natural extension of the CCE for two player
    games. In fact, if we consider the NA game to be a two player game with no self-loops, then
    we recover exactly the definition of the CCE set in two player games \cite{Ostrovski2014}.
  \end{remark}

  \begin{remark}
    The notion of the CCE set is related to the idea of \emph{average external regret} (for the
    sake of brevity we drop the term `external' and refer the reader to \cite{Nisan2007}). Here, we
    will present what is meant by average regret and state that if at some time $T$ all agents'
    average regret is non-positive, then the game is said to have reached the CCE set. The
    reader should consult \cite{Ostrovski2014} for an excellent exposition regarding the
    link between the CCE set and average regret in two player games which, of course, extends
    naturally to the NA game.

@@

    in which $\pure{\mu}{i}$ denotes the probability vector in $\Delta_\mu$ with $1$ in the slot
    $i'$ and $0$ everywhere else. Note, this is the \emph{average regret} for the agent $\mu$
    and, of course, can be related to the \emph{cumulative regret} which is used for analysis
    in \cite{Leonardos2020, Cesa-Bianchi2021}.  To illustrate the average regret, let us
    consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
    is given by

@@

  As a example of nonconvergence we consider the Shapley family of games \cite{Shapley2016}. In a two player bimatrix game $(A_\beta, B_\beta)$ this is given by

@@

  where $\beta \in (0, 1)$. In \cite{VanStrien2011} this was shown to produce both periodic and chaotic behaviour for different choices of $\beta$.

@@

\bibliographystyle{acm}
\bibliography{references}
